### 2016-03-02 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Edits to intro. section of FDS Exp Report

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
[FDS intro, importance of validation, fact this report only includes experimental setup and procedure]

@@

\subsubsection*{East Structure}
Three different test series---Series 4, Series 5, and Series 6---were conducted in the east structure. Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure. The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern. During the experiments in Test Series 5, each double door was opened and the roof vent was opened and closed throughout the procedure. Both the roof vent and west double door were opened during each experiment in Series 6. Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} outline the experimental procedures of Test Series 4--6 in more detail.

@@

\subsubsection*{West Structure}
Two different test series---Series 22 and Series 24---were conducted in the west structure. Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure. Experiments conducted during Series 22 followed a procedure in which each double door on the first and second floors was opened. Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure. Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} outline the experimental procedures of Test Series 22 and 24 in more detail.

>>>>

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
% [FDS intro] 
Fire dynamics 
% [importance of validation]

% [this report is (1/2) --> experimental setup and procedure]
This report describes the full-scale fire test experiments that are used for the FDS model validation of [...]. Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings. During each test, propane was provided to three burners at a known flow rate [to create a diff flame]. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected.

@@

\section{East Structure Tests}
Three different test series---Series 4, Series 5, and Series 6---were conducted in the east structure. Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure. The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern. During the experiments in Series 5, each double door was opened and the roof vent was opened and closed. Both the roof vent and west double door were opened during each experiment in Series 6. Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} include a schematic and additional details about the procedures used for the experiments during Series 4--6.

@@

\section{West Structure Tests}
Two different test series---Series 22 and Series 24---were conducted in the west structure. Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure. Experiments conducted during Series 22 followed a procedure in which each double door on the first and second floors was opened. Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure. Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} include a schematic and additional details about the procedures used for the experiments during Series 22 and 24.
